{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2023-11-01 paper/si.tex
use \strategy in SI

We assume that the players' payoff received from their last interaction is their
expected payoff given by Eq.~\eqref{eq:expected_payoff}. Thus, a resident
interacting with a resident receives the payoff $\pi(s_\resident, s_\resident)$,
and $\pi(s_\resident, s_\mutant)$ when interacting with a mutant. Similarly, a
mutant interacting with a resident receives the payoff $\pi(s_\mutant,
s_\resident)$ and $\pi(s_\mutant, s_\mutant)$ when interacting with a mutant.\\

>>>>

We assume that the players' payoff received from their last interaction is their
expected payoff given by Eq.~\eqref{eq:expected_payoff}. Thus, a resident
interacting with a resident receives the payoff $\pi(\strategy_\resident, \strategy_\resident)$,
and $\pi(\strategy_\resident, \strategy_\mutant)$ when interacting with a mutant. Similarly, a
mutant interacting with a resident receives the payoff $\pi(\strategy_\mutant,
\strategy_\resident)$ and $\pi(\strategy_\mutant, \strategy_\mutant)$ when interacting with a mutant.\\
